---
title: "Introduction to R: Assignment 01"
author: "YOUR NAME HERE [YOUR ROLL NUMBER HERE]"
output: html_document
---

# INSTRUCTIONS AND ADVICE

* **Soft Deadline:** 25 August (8pm)
* **Hard Deadline:** 26 August (8am)
* There are ten questions in this assignment. Each question carries two      points.
* This assignment accounts for 20% of your final grades.
* You are allowed/encouraged to collaborate with others, but the final
  submission must be your own original work. Please do write name(s) of
  your collaborators.
* The file must be submitted via Canvas in the following format-
   xxx.Rmd where xxx is your three-digit roll number.
  


# 1

From the excel file shared with you, pick a date from the file,
create an object storing that date.


```{r}
#### TYPE YOUR CODE HERE
date.vec <- as.Date("2020-06-25")
```


# 2

Create a vector that represents the total number of covid19 cases for
at least six different states in the country on your chosen date. 
You can name it whatever you want.

```{r}
#### TYPE CODE HERE
vector1 <- c(80858, 33926, 26210, 34178, 199749, 7493, 22693,53973)
states <- c("AP", "BI", "MP", "RA", "TN", "JH", "OD", "WB")
names(vector1) <- states
print(vector1)
```

# 3

What is the average number of covid19 cases in your vector? 
Find out in two ways, with and without using the `mean()` command.


```{r}
#### TYPE CODE HERE
ave_vector1 <- sum(vector1)/length(vector1)
print(ave_vector1)
mean_vector1 <- mean(vector1, na.rm = T)
print(mean_vector1)
```


# 4

Which of those states has least number of cases? How many cases does it have? (Use an `R` command to find out.)


```{r}
#### TYPE CODE HERE
print(paste(names(vector1)[which.min(vector1)], 
            "has", min(vector1), "cases"))

```

# 5

What is the difference in the number of covid19 cases between the worst-affected state and the least affected state (relatively speaking) in your vector? 
(Again use `R` to find out, and try to be as general as possible in the sense that your code should work even if the elements in your vector, or their order, change.)

```{r}
#### TYPE CODE HERE
diff.cases <- max(vector1) - min(vector1)
print(diff.cases)


```

# 6

How many states in your vector have above 10000 cases? 
(Again, try to ensure your code work even in the case that your vector changes.)

```{r}
#### TYPE CODE HERE
print(paste("The number of states with more than 10,000 cases is:",
            length(vector1[vector1>10000])))


```


# 7
Create a new vector that contains cases per 100,000 population. You will need to figure out state populations from Wikipedia. Make sure that the
numbers in the new vectors are rounded off to one decimal place.

```{r}
#### TYPE CODE HERE
pop.states <- c(49577103, 104099452, 
                72626809, 68548437, 
                72147030, 32988134, 
                41974219, 91276115)
percapitacases <- round(vector1/pop.states*100000, 1)

```


# 8

Create a new vector with a random sample of 3 states from your original vector. What is the average number of covid19 cases in this new vector?

```{r}
#### TYPE CODE HERE
rand.cases <- sample(vector1, 3)
mean_rcases <- round(mean(rand.cases),1)
print(mean_rcases)

```

# 9

Create a new vector where you set the number of cases in your original vector (question number 2) to zero if the number of cases is less than 1000.

```{r}
#### TYPE CODE HERE
new_vec <- vector1
new_vec[new_vec < 1000] = 0
print(new_vec)
```

# 10

Generate a vector that contains the logarithm of the number of cases using your original vector (question number 2). List all the vectors you have created in this exercise.

```{r}
#### TYPE CODE HERE
log_cases <- log(vector1)

ls()
```


# COLLABORATORS
Create a vector (and print) containing the names of your collaborators for this assignment.
```{r}
#### TYPE CODE HERE
collaborators <- paste("with", "a little", "help","from my friends")
print(collaborators)
```