---
title: "Introduction to R: Assignment 01"
author: "YOUR NAME HERE [YOUR ROLL NUMBER HERE]"
output: html_document
---
  
# INSTRUCTIONS AND ADVICE
  
* **Soft Deadline:** 24 September (8am)
* **Hard Deadline:** 25 September (8am)
* There are ten questions in this assignment. Each question carries two      points.
* This assignment accounts for 30% of your final grades.
* You are allowed/encouraged to collaborate with others, but the final
  submission must be your own original work. Please do write name(s) of
  your collaborators.
* The file must be submitted via Canvas in the following format-
  xxx.Rmd where xxx is your three-digit roll number.
* Some guidelines-
   
  - Please make sure that you print your answer.

  - Please do not put your folder path anywhere in the code.

  - Please avoid tinkering with the structure of the file.
  
  - Write your code only in the space provided.

  - Write your name and your roll number at the top in the space
    provided.
    
  - I reserve the right to award zero in case these guidelines 
    are not followed.

```{r echo=F, message=F}  
# Load packages here
pacman::p_load(tidyverse, readxl)

```


Read the csv file in $\texttt{R}$, and answer questions 1-6 using the data `cricdata`.

```{r message=F}
# Read the data
cricdata <- read_csv("IndBatRec.csv")
```

# 1

Clean the following columns `100`, `50`, `0` and assign them standard object names (recall that standard names in $\texttt{R}$ usually start with alphabets). 

```{r}
# Write your code here


```


# 2

Pick a year. Who were the top 5 batsmen (yardstick: `Runs`) in your chosen year? Calculate the total runs scored by these batsmen.

```{r}
# Write your code in this space.

```

# 3 
Pick a cricketer who appears in the data frame at least five times, and calculate the average runs scored by this batsman.
(Hint: The average runs should be total runs divided by total number of innings.)

```{r}
# Write your code in this space. 

```

# 4
For each decade starting from the year 1980 (80s, 90s, etc.), print the list of the batsmen who hit the maximum number of sixes.
```{r}
# Write your code in this space

```

# 5
Choose two years between 1980 and 2019 with a minimum gap of ten years (example: pick 1991 and 2001). Make a data frame for the top run-getter for each year between the two years (including the two years).
```{r}
# Write your code in this space

```


# 6 
Use chain to do the following:

 - **Step 1**: Pick five consecutive years (randomly).
 - **Step 2**: Select name, innings, and runs scored.
 - **Step 3**: Calculate average runs.
 - **Step 4**: Sort the data by average runs in descending order.

```{r}
# Write your code in this space

```


# 7 

I have loaded a dataset called `towns`. The dataset contains two columns- `City` (name) and `TOT_P`(population). Create a new column
called `pop_bin` which takes the following values-
 
 - when `TOT_P` <= 1 lakh : 1
 
 - when `TOT_P` ranges between 1 and 5 lakh: 2
 
 - when `TOT_P` ranges between 5 and 10 lakh: 3
 
 - when `TOT_P` lies between 10 and 30 lakh: 4
 
 - when `TOT_P` > 30 lakh: 5
```{r, message=F}
towns <- read_csv("towns.csv")

# Write your code here

```

# 8

Following up on Q7, create a table using the variable `pop_bin` which
tells us the number of towns in each bin. 

```{r}
# Write your code here

```


# 9

The dataset `evalData` contains the student evaluation data for the course titled "Introduction to a Really Boring Subject" taught by Professor Grumpy.
Tidy `evalData`. Do you need to make it wider or longer? What are the variables?
```{r, message=F}
evalData <- read_csv("courseEval.csv")
# Write your code here

```

# 10
From the new tidy data pick any one metric and produce a table which looks like the table shown below.

| Question| Rating | Count | Percent |
| :------------- | :----------: | -----------: | -----------: |
|1629: Lecture Clarity | 1 | 20 | 20 |
|1629: Lecture Clarity | 2 | 20 | 20 |
|1629: Lecture Clarity | 3 | 30 | 30 |
|1629: Lecture Clarity | 4 | 20 | 20 |
|1629: Lecture Clarity | 5 | 10 | 10 |


```{r}
# Write your code here

```
  


# COLLABORATORS
Create a vector (and print) containing the names of your collaborators for this assignment.
```{r}
#### TYPE CODE HERE

```